\section{Complex Numbers}

\subsection{Arithmetic Operations}

\subsubsection{Exercise 3}
This exercise is much easier if we represent the complex numbers in polar form (which has not been introduced
yet). We see that
\begin{align*}
        \frac{-1 \pm i \sqrt{3}}{2} &= e^{i \frac{2\pi}{3}}, \: e^{i \frac{4 \pi}{3}} \\
        \frac{\pm 1 \pm i \sqrt{3}}{2} &= e^{i \frac{2\pi}{3}}, \: e^{i \frac{4 \pi}{3}}, \:  
        e^{i \frac{\pi}{3}}, \: e^{i \frac{5 \pi}{3}} \\
\end{align*}
which gives us the desired equality since $e^{i 2\pi} = 1$.

\subsection{Square Roots}
Once again, all of these computational exercises are made much easier with polar form. 
They seem more tedious than instructive.

\subsection{Justification}
Going to come back to this after finishing chapter 3 of Birkhoff/MacLane (which I've been neglecting...).

\subsection{Conjugation, Absolute Value}

\subsubsection{Exercise 3}
We can manipulate the equality to get
\begin{align*}
        \norm{\frac{a - b}{1 - \bar{a}b}} &= 1 \\
        \norm{a - b}^2 &= \norm{1 - \bar{a}b}^2 \\
        \norm{a}^2 + \norm{b}^2 - 2\Re(a\bar{b}) &= 1 + \norm{a}^2 \norm{b}^2 - 2\Re(a\bar{b}) 
\end{align*}
Thus we see that equality holds if either $\norm{a} = 1$ or $\norm{b} = 1$, excepting the case where 
$a = b = 1$ as that makes the denominator in the equality 0.

\subsubsection{Exercise 4}
Let $z = \alpha + \beta i$. Then we have
\begin{align*}
        \big((a + b) \alpha + c\big) + (a - b)\beta i &= 0 \\
        \implies (a + b) \alpha + c &= 0 \\
        \implies (a - b) \beta = 0
\end{align*}
If $a - b = 0$, $\beta$ could be anything, so we must have $a - b \neq 0$ for the solution to be unique.
Similarly, if $a + b = 0$ then $\alpha$ can either be anything or there is no solution for $\alpha$ 
(if $c \neq 0$). Thus, the two conditions we need are  $a + b \neq 0$ and $a - b \neq 0$.

\subsubsection{Exercise 5}
We can write $\abs{\sum_{i = 1}^n a_i b_i}^2$ as $(\sum_{i = 1}^n a_i b_i) (\sum_{j = 1}^n \overline{a_j b_j})$
to see that it can be expanded as a sum whose terms consist of $\abs{a_i}^2 \abs{b_i}^2$ and 
$a_i b_i \overline{a_j b_j}$ over all $1 \leq i, j \leq n$. The $a_i b_i \overline{a_j b_j}$ terms can be
paired with the $a_j b_j \overline{a_i b_i}$ terms to get that
\begin{align*}
        \abs{\sum_{i = 1}^n a_i b_i}^2 &= \sum_{i = 1}^n \abs{a_i}^2 \abs{b_i}^2 + \sum_{1 \leq i < j \leq n} 2 \Re a_i b_i \overline{a_j b_j} \\
                                       &= \sum_{i = 1}^n \abs{a_i}^2 \sum_{i = 1}^n \abs{b_i}^2 - \sum_{1 \leq i < j \leq n} \abs{a_i \bar{b}_j - a_j \bar{b}_i}^2
\end{align*}

\subsection{Inequalities}

\subsubsection{Exercise 3}
We apply the triangle inequality and then Cauchy-Schwarz to get
\begin{align*}
        \abs{\sum_{i} \lambda_i a_i} \leq \sum_{i} \abs{\lambda_i a_i} \leq \sum_{i} \abs{\lambda_i} \abs{a_i} < \sum_{i} \abs{\lambda_i} = 1
\end{align*}
Where the final strict inequality follows from $\abs{a_i} < 1$.

\subsubsection{Exercise 4}
We have that $\abs{z - a} = \abs{z} - \abs{a}$ when $\frac{z}{a} \geq 1$ (applying our criterion for equality
to $\abs{(z - a) + a}$). Thus, if $\abs{a} \leq \abs{c}$, we can choose $z$ such that $\frac{z}{a} \geq 1$ 
and $\abs{z} = \abs{c}$, so a solution to the equation exists. Now suppose a solution exists to 
 $\abs{z - a} + \abs{z + a} = 2\abs{c}$. Then by applying the triangle inequality, we have 
 \begin{align*}
         2\abs{c} \geq \abs{z - a} + \abs{z + a} \geq \abs{z - a - z - a} = 2\abs{a}
 \end{align*}
 so $\abs{a} \leq \abs{c}$.

\subsection{Geometric Addition and Multiplication}

\subsubsection{Exercise 2}
We will only show one direction, since the other direction just reverses the steps. Suppose that 
$a_1, a_2, a_3$ indicate the vertices of an equilateral triangle. Then the angles between the edges
$a_1 - a_3, a_3 - a_2, a_2 - a_1$ must be equal. Using the fact that $\text{arg} \frac{a_2}{a_1} = \text{arg} a_2 - \text{arg} a_1$, we get
\begin{align*}
        \frac{a_1 - a_3}{a_3 - a_2} &= \frac{a_3 - a_2}{a_2 - a_1} \\
        a_1 a_2 - a_1^2 - a_2 a_3 + a_3 a_1 &= a_3^2 - 2 a_2 a_3 + a_2^2 \\
        a_1 a_2 + a_2 a_3 + a_3 a_1 &= a_1^2 + a_2^2 + a_3^2
\end{align*}

\subsubsection{Exercise 4}
Let the center of the circle be $c$. Then we can proceed similarly to Exercise 2 by noting that since
$\abs{c - a_1} = \abs{c - a_2} = \abs{c - a_3}$, we have that the angle between $c - a_1$ and $a_1 - a_3$ 
is the same as the angle between $a_1 - a_3$ and $a_3 - c$. We can then solve for $c$ and use $c$ to compute
the radius. The result, though, is messy and not fun to typeset.

\subsection{The Binomial Equation}

\subsubsection{Exercise 4}
Let $s = 1 + w^h + ... + w^{(n - 1)h}$. Then we have that $w^h s = w^h + w^{2h} + ... + w^{nh}$, which implies
that $w^h s = s$ since $w^{nh} = 1$. If $h$ is not a multiple of $n$, then $w^h \neq 1$, so $s = 0$.

\subsubsection{Exercise 5}
The approach is the same as Exercise 4. Letting $s$ denote the sum, we multiply by $-w^h$ to get that
$-w^h s = (-1)^n - w^h + ... + (-1)^{n - 1} w^{(n - 1)h}$. Thus, $s = 0$ if $n$ is even (even if $w^h = -1$).
Otherwise, we solve $-w^h s = s - 2$ to get that $s = \frac{2}{1 + w^h}$ ($w^h \neq -1$ since $n$ is odd).

\subsection{Analytic Geometry}

\subsubsection{Exercise 1}
We refer back to Exercise 4 from the section ``Conjugation, Absolute Value''. If $z = \alpha + \beta i$, then
\begin{align*}
        (a + b) \alpha + c &= 0 \implies \alpha = -\frac{c}{a + b}\\
        (a - b) \beta &= 0
\end{align*}
If $a - b = 0$, then $z = -\frac{c}{a + b} + ti$ for all $t \in \mathbb{R}$, which is a line.

\subsubsection{Exercise 2}
We have the following:
\begin{itemize}
        \item Ellipse: Given foci $f_1, f_2$, we can write the equation as $\abs{z - f_1} + \abs{z - f_2} = 2a$.
        \item Hyperbola: Given foci $f_1, f_2$, we can write the equation as
                $\abs{\abs{z - f_1} - \abs{z - f_2}} = 2a$.
        \item Parabola is a little trickier, since now we're concerned with distance to a point (focus) as
                well as the distance to a line (directrix). One can compute the minimum distance to the
                directrix using a number of methods (calculus, complex inner product, etc.). Out of laziness
                I'm just going to call the distance to the directrix $\abs{z - d}$. Then we have that the
                equation for a parabola looks like $\abs{z - f} = \abs{z - d}$.
\end{itemize}

\subsection{The Spherical Representation}

