\section{Determinant and Trace}

\subsection{Exercise 1}
(a) The discriminant already has ordered versions of all the $(i, j)$ difference terms.
Applying a permutation only changes the signs of some of the difference terms, hence
$\sigma(p) = 1, -1$.

(b) $\sigma(p_1 \circ p_2) = \text{sign}(P(p_1 \circ p_2 (x_1, ..., x_n)))  = \sigma(p_1) \text{sign}(P(p_2 (x_1, ..., x_n)))$.

\subsection{Exercise 2}
(c) A transposition swaps two indices, and hence flips the sign of their associated
difference term in the discriminant.

(d) If $p(i) = j$, then we can start with the permutation $(i \: j)$.
Next, if $p(j) = k$, we can compose with  $(i \: k)$ to get $(i \: k) \circ (i \: j)$.
We can do this until we have completely reconstructed the permutation using
transpositions.

\subsection{Exercise 3}
By starting with a different $i$ in Exercise 2 (d), we can obtain a different
decomposition of transpositions. However, the parity of the decomposition must
be the same, as otherwise $\sigma(p)$ will take on two different values for
the same $p$.

\subsection{Exercise 4}
(Property II): Each term in $D(a_1, ..., a_n)$ contains exactly one element
from each of the $a_i$. Thus, scaling any of the $a_i$ by $k$ scales the entire
determinant by $k$. Similar logic for vector addition.

(Property III): The only non-zero term in $D(e_1, ..., e_n)$ is associated with
the identity permutation, hence $D(e_1, ..., e_n) = 1$.

(Property IV): Swapping two arguments is the same as applying a transposition to
each of the terms in $D(a_1, ..., a_n)$, which flips the sign of $D$.

\subsection{Exercise 5}
Suppose $a_1 = a_2$. Then:
\begin{align*}
        D(a_1, a_2, ..., a_n) &= -D(a_2, a_1, ..., a_n) \\
        D(a_1, a_2, ..., a_n) + D(a_1, a_2, ..., a_n) &= 0
\end{align*}

\subsection{Exercise 6}
We can swap rows and columns until $A$ is in the same form as in Lemma 2.
Since each row and column swap is equivalent to applying a transposition,
we get that $\det A = (-1)^{i + j} \det A_{ij}$.

\subsection{Exercise 7}
Each term in the sum $D(a_1, ..., a_n) = \sum \sigma(p) a_{p_1 1} ... a_{p_n n}$ consists of
exactly one element from each column and each row; swapping rows and columns does not
change the terms in the sum. However, the permutation associated with each term is changed.
The permutation $p$ that sends $1 \to p_1$ becomes $p'$ sending $p_1 \to 1$. This $p'$ 
is exactly $p^{-1} $. Since $\sigma(1) = \sigma(p^{-1}  \circ p) = \sigma(p^{-1}) \sigma(p)$, 
$\sigma(p^{-1}) = \sigma(p)$ we are done.

\subsection{Exercise 8}
$P$ is the linear transformation such that $P(e_j) = e_i$; in other words,
$P$ rearranges the representation of $x$ by applying $p$ to the components of $x$.
We also have that $PQx = P q(x) = p \circ q(x)$, since $Qx$ permutes the components
of $x$ to produce $q(x)$, and $P q(x)$ permutes the components of $q(x)$ to produce
$p \circ q(x)$.

\subsection{Exercise 9}
\begin{align*}
        &\Tr AB = \sum_{i = 1}^m (AB)_{ii} = \sum_{i=1}^m \sum_{j=1}^n a_{ij}b_{ji} \\
        &\Tr BA = \sum_{j=1}^n (BA)_{jj} = \sum_{j=1}^n \sum_{i=1}^m b_{ji} a_{ij}
\end{align*}

\subsection{Exercise 10}
\begin{align*}
        \Tr A A^{\top} &= \sum (A A^{\top})_{ii} = \sum \sum a_{ij} a^{\top}_{ji} \\
                       &= \sum \sum a_{ij}^2
\end{align*}

